### 2018-04-10 latex/icpp18/experiments.tex
progress

\section{Experiments}
\label{sec:experiment}
\newcommand{\NLS}{LUC }
\newcommand{\krfaun}{\textbf{COL}\xspace}
\newcommand{\krcun}{\textbf{CN}\xspace}

@@

\subsection{Experimental Setup}
In this paper, we use both synthetic and realworld datasets. The synthetic datasets are used to evaluate the communication
 strategies with the increase in number of non-zeros of the sparse matrices. 
\subsubsection{Datasets}\label{sec:datasets}

@@

\subsection {Effect of partitioning strategies}

>>>>

\section{Experiments}
\label{sec:experiment}
\newcommand{\NLS}{LUC }
\newcommand{\krfaun}{\textbf{COL}\xspace}
\newcommand{\krcun}{\textbf{CN}\xspace}
\newcommand{\krcr}{\textbf{CR}\xspace}
\newcommand{\krch1}{\textbf{CH1}\xspace}
\newcommand{\krch2}{\textbf{CH2}\xspace}

@@

\subsection{Experimental Setup}
In this paper, we use both synthetic and realworld datasets. The synthetic datasets are used to evaluate the communication
 strategies with the increase in number of non-zeros of the sparse matrices. 
 We used PaToH~\cite{caay:99} for partitioning hypergraphs.
\subsubsection{Datasets}\label{sec:datasets}

@@

\subsection {Effect of partitioning strategies}
In \cref{fig:nnzsweepcomm}, our first observation is that all partitionings except \krfaun yield comparable results in terms of communication, while there is some variation  in the computation times provided in \cref{fig:nnzsweepcomp}.

\krcun gives similar k
